\chapter{Executive Board}
\label{art:exec}

\begin{enumerate}[label=\Alph*.]

\item The Executive Board shall comprise of a President, Vice President, Chair for Finance, 
Chair for Social Programming, and a Chair for Logistics.
\item The election for the Executive Board shall take place in the last General Assembly meeting of Spring Semester. The call for nominations shall be announced no less than two weeks before the
election date. The Vice President or their designee shall conduct the elections.
\item The term for the Executive Board members shall be from 1st May following their election to
30th April of the following year.  
\item A member of the Executive Board may serve as a representative for a department or a
program during their term, but will only be granted a single vote in the General Assembly.
\item The Executive Board may act on behalf of the General Assembly when the General Assembly is
not in session to address any issue that impacts GSEG or its members.
\item The Executive Board members may appoint individuals to assist them in their role.

\item The Executive Board shall meet at least once each month. It shall also meet on the call
of the President or by a petition of half of its members. 

\item All Executive Board members shall attend all Executive Board meetings and General Assembly
meetings. More than two unexcused absences per year are grounds for dismissal.

\item The President shall preside over the General Assembly meetings and Executive Board meetings. In conjunction with the Executive Board, they shall devise and implement annual goals and strategies to fulfill GSEG's mission. The President shall delegate such responsibilities as appropriate to other members of the Executive Board. 

\item The President shall be the primary GSEG representative to all the School and University administration and personnel, and shall attend all meetings with such personnel as necessary and appropriate.

\item The Vice President shall be responsible for organizing the General Assembly meetings and Executive Board meetings and distributing the agendas and resolutions as described in Article~\ref{art:assembly}, clause \ref{assembly-vp}

\item The Vice President shall act as an interim President when the President is unable to execute the duties of their office. If the Vice President is unable or unwilling to serve as an interim President, one of the Chair/s for Finance shall serve as an interim President.

\item The Chair for Finance Chair shall deal with all budgetary issues, the distribution of reimbursements, event ticketing, and collection of receipts for GSEG expenditures. They shall budget, allocate, and monitor funds dispersed under the auspices of funding policies established by the GSEG.

\item The Chair for Social Programming shall organize academic, cultural, outreach, recreational, and social events that align with the annual goals and strategies of GSEG. 

\item The Chair for Logistics shall record the minutes, monitor attendance, as well as certify quorum of all General Assembly and Executive Board meetings.

\item The Chair for Logistics shall maintain the GSEG website, draft and distribute the GSEG newsletter, as well as manage all GSEG accounts related to communication and media. 

\item In case of a vacancy for an Executive Board member, there shall be a special election in a meeting of the General Assembly. The call for nominations shall be announced no less than two weeks before the date of the special election. The Vice President or their designee shall conduct the special election.

\item A member of the Executive Board who is found in the violation of this constitution may be removed upon an impeachment motion moved with two-thirds vote in the General Assembly. Just cause, that is, malfeasance, misfeasance, or nonfeasance, must be shown in any case involving removal of an Executive Board member.

\end{enumerate}


