\chapter{GAPSA Representatives}
\label{art:gapsa-reps}

\begin{enumerate}[label=\Alph*.]
\item The GSEG General Assembly shall represent its members at the Graduate and Professional Student Assembly (GAPSA) during the Fall and Spring semesters through elected representatives to the General Assembly of GAPSA. 
\item The elections for GAPSA representatives shall take place in the first General Assembly
meeting of the Fall Semester. The call for nominations shall be announced no less than two weeks 
before the date of the election. The elections shall be conducted by the Vice President or their
designee. 
\item The term for GAPSA representatives shall be from the day of their election to the end of 
Spring Semester. 
\item In the period between the end of Spring Semester and the GAPSA representative elections in the following year, the President or their designee shall serve as the GAPSA representative. 

\item GAPSA representatives shall attend all General Assembly meetings. More than two unexcused
absences per semester are grounds for dismissal. 

\item GAPSA representatives shall abide by this Constitution. A representative found to violate this Constitution shall be given a notice stating the violation no less than five days before the following General Assembly meeting. Just cause (malfeasance, misfeasance, or nonfeasance) must be shown in all cases involving the dismissal of a GAPSA representative.

\item In case of a vacancy for GAPSA representative, the Executive Board shall appoint an interim
representative and conduct a special election in a meeting of the General Assembly. The call for
nominations shall be announced no less than two weeks before the date of the special election.
The special elections shall be conducted by the Vice President or their designee. 
\end{enumerate}